Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-07-15 writeup/rocha_etal.tex
Fixes capitalization of ECCO2 in Menemenlis reference

  \bibitem[{\textit{Menemenlis et~al.}(2008)\textit{Menemenlis, Campin, Heimbach,
    Hill, Lee, Nguyen, Schodlok, and Zhang}}]{menemenlis_etal2008}
  Menemenlis, D., J.-M. Campin, P.~Heimbach, C.~Hill, T.~Lee, A.~Nguyen,
    M.~Schodlok, and H.~Zhang (2008), Ecco2: High resolution global ocean and sea
    ice data synthesis, \textit{Mercator Ocean Quarterly Newsletter},
    \textit{31}, 13--21.

>>>>

  \bibitem[{\textit{Menemenlis et~al.}(2008)\textit{Menemenlis, Campin, Heimbach,
    Hill, Lee, Nguyen, Schodlok, and Zhang}}]{menemenlis_etal2008}
  Menemenlis, D., J.-M. Campin, P.~Heimbach, C.~Hill, T.~Lee, A.~Nguyen,
    M.~Schodlok, and H.~Zhang (2008), ECCO2: High resolution global ocean and sea
    ice data synthesis, \textit{Mercator Ocean Quarterly Newsletter},
    \textit{31}, 13--21.
